Amazonian Narratives in Presidential Discourse (1985 to 2020)

### 2021-11-05 08112021_Sposito & Silva_Muller_DRAFT.Rmd

library(dplyr)
library(stringi)
library(tm)
library(ggplot2)
library(tidytext)
library(kableExtra)
library(stringr)
library(wordcloud)
library(RColorBrewer)

# Load data
#BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path

# Subset for text matches
Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("Amazôn|Amazon|amazôn|amazon", text))
# Remove accents and extra spaces
Amazon_speeches$text <- stringi::stri_trans_general(Amazon_speeches$text, id = "Latin-ASCII")
# Make all lower case
Amazon_speeches$text <- tolower(Amazon_speeches$text)
# Remove extra white spaces
Amazon_speeches$text <- tm::stripWhitespace(Amazon_speeches$text)
# Get only the pertinent text chunks
Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
# Transform into a single text per row...
Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))

@@

## Including Plots

You can also embed plots, for example:

>>>>

library(dplyr)
library(stringi)
library(tm)
library(ggplot2)
library(tidytext)
library(kableExtra)
library(stringr)
library(wordcloud)
library(RColorBrewer)
library(tidyr)

# Load data
#BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
#Amazon_speeches <- readRDS("~/GitHub/amazondef/amazon_speeches.Rds")
BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
Amazon_speeches <- readRDS("~/Documents/GitHub/amazondef/amazon_speeches.Rds") #livio's path

# Subset for text matches
#Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("Amazôn|Amazon|amazôn|amazon", text))
# Remove accents and extra spaces
#Amazon_speeches$text <- stringi::stri_trans_general(Amazon_speeches$text, id = "Latin-ASCII")
# Make all lower case
#Amazon_speeches$text <- tolower(Amazon_speeches$text)
# Remove extra white spaces
#Amazon_speeches$text <- tm::stripWhitespace(Amazon_speeches$text)
# Get only the pertinent text chunks
#Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
# Transform into a single text per row...
#Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
#saveRDS(Amazon_speeches, file="amazon_speeches.rds")

@@
